\section{Introduction}

In the past few years, significant progress has been made in stronger abstract game playing agents,
the artificial intelligence (AI) controller of game agent is much more stronger to be able to beat the top
professional human players such as Alpha Go, while the Real-Time Strategy (RTS) game is different and
more complicated from abstract game as chess, the actions that different game agents assigned could be
simultaneous, in some situations the player only have the partial vision and size of game state and game
area, due to the game state changes at per game time, the available and possible order actions of each
game units are limited in different game state. Every imperceptible change of game state could result in
a totally different game ending. Because of those factors that is difficult and complex for artificial
intelligence host to judge and make decision of the game, human players are usually stronger than the AI bots.

The bot that our group created is based on a simple type of RTS game which called microRTS, microRTS is a
two-player game build on several different grid map, each player of the game could control units and assign
actions to them for the final goal of destroying each units of the opponent. In microRTS, the basic elements
include resource, building and moving units, the resource is the initial immovable units on the map, which
could be harvested to producing new units. The building units include base and barrack which are fixed on
the map, base and resource are both the initial units of the game, base could produce worker and barrack
could produce other attack units. The moving units include worker, light, heavy and ranged, worker can only
be produced by base and barrack produced other three types of units. The duty of worker is to harvest resource
and build new buildings, worker does have the attack ability but the damage is low. Other three attack units
which produced by barrack divided into light, heavy and ranged. As the name suggests, light has high movement
speed and considerable damage points, heavy has the highest damage point and hit point but the lowest movement
speed, ranged has lower hit points but the maximum attack range.

Although the microRTS has the reduced units and simpler game state than other complex RTS game as StarCraft,
the decision space is still huge. The game map is rectangular grid-based map of arbitrary size, each grid represent
a movement unit. The initial game state is variant that resource and base could be anywhere, sometimes the resource
might separate the map to two parts, each side set up a player, which means the player could not get to their opponent
directly. In some initial map the resource is lack, some there is an built-in barrack near the base. While those are
just the complexity of the initial state, if the initial game state is set as the root of the decision tree, each
change of the game state will increase the branch of the decision tree with the game goes on. In order to defeat
the opponent, it is necessary to build a bot strategy that adapts the volatile situation. The aim of our group is
to construct such a bot strategy which is strong enough to beat the opponent of variant game state, the bot we create
using the decision tree to judge the game state and make actions. Through the test, the bot we create is able to defeat
all the built-in bot on four given testing map.
