\section{Benchmark}

Our tactical bot extends built-in class 'WorkerRushPlusPlus', the reason will be
demonstrated later in details, we override some methods and changed the 'PlayerAction'
behaviour, at last we would test our bot with built-in strategies to measure the effectiveness.

There were few difficulties during building our intelligent bot, the most awkward
one is the path-finding problem. In our pre-defined behaviour tree, the bot has to
judge whether there is an available road to destination, there was an existing method
of path-finding, this method bases on a moveable unit to find the way, but in the map
'NoWhereToRun9x8', there is only one base at beginning, which always leads to the wrong
judgement of path-finding state and the bot behaviour did not meet our expectation. So
we rewrote the path-finding method in our code, considering the road between two coordinates
existing or not. Then the problem was fixed.

Another problem appeared during the test of map 'NoWhereToRun9x8'. In our strategy, the
barrack would keep training attack units until the road to enemy is clear, while the
barrack would crashed when it is surrounded by units. So we changed the rules of units
'Standby', make them would move to nearest grid to make the way when they 'notice' they
are near the barrack or other unit.

One of the most important factor of win the battle is finance. In this game it represents
the harvesting efficient, a large amount of workers is not necessarily the best to the speed
of obtaining resource. In some situations too many workers might block the road, sometimes
producing workers would overuse resource of training attack units. So a balance relation
between worker amount and game state is necessary. In our strategy, we consider the minimum
value between base amount times 2 and resource unit amount times 1.5 as worker amount. But
some times the resource unit might at corner or surrounded by other resource, which could
leads to wrong judgement and produce redundant workers then reduce efficiency. We solved this
problem by using the path-finding method we rewrote before to judge whether the worker is able
to get to the resource first to count the available resource, then all the workers are on their
duty.
