\section{Experimental Study}

Before we design the behaviour tree of our intelligent battle bot, we have conducted
several test between the built-in strategies to decide which strategy is better within
specific game state and customize our unique strategy for the bot to achieve better
performance on the battle field. The built-in bot we have tested consist of WorkerRush (WR),
WorkerDefence (WD), WorkerRushPlusPlus (WR++), HeavyRush (HR), HeavyDefence (HD),
LightRush (LR), LightDefence (LD), RangedRush (RR), RangedDefence (RD) and
SimpleEconomicRush (SER). First we test the map of 'basesworkers16x16', the
competition was set between different Rush strategies(exclude Defence strategies), the
testing result is shown in the Table \ref{table:basesworkers16x16}.

\input{tables/chap06_basesworkers16x16.tex}

From the Table \ref{table:basesworkers16x16}, we noticed that on this battle map the built-in
bot with 'WorkerRushPlusPlus' strategy presents the highest combat effectiveness. The difference
between strategy 'WorkRush' and 'WorkRushPlusPlus' is the harvest efficient, result in
'WorkerRushPlusPlus' perform better than 'WorkRush' on this map. The testing result is similar
on the map 'baseworkers24x24H', the reason we speculate is although the size of battle map is
expanded, the transformation is not enough to turn the table. Through the observation of fighting
procedure, we noticed that the scale and initial condition such as the number of resource and
whether there exists barracks near the base at the begin of the map are major cause of why
'WorkerRushPlusPlus' perform so good. Even though worker is definitely not the best choice to
fight, worker still has the attack ability, with the advantages of high movement speed and low
production cost of resource and time, a flood of workers could be an army with destructive force
in the map with small scale, with the observation of battle between 'WorkerRush' and strategies
which have priority to build barracks when there is no barrack such as 'SimpleEconomicRush', the
workers always get to the opponent's buildings and cause damage before the opponent's barrack construction
complete. The situation changed in a map of larger scale, if the worker failed to destroy opponent's
barracks or bases before the first training of attack units as heavy, light or ranged finished, the
situation is reversed, 'WorkerRush' bot would be defeated finally. From the above, the strategy
'WorkerRushPlusPlus' is invoked by our tactical bot after the judgement of map scale and barracks
state, if map size is not large enough and no barracks at beginning, do 'WorkerRushPlusPlus'.

We run the test between 'Rush' and 'Defence' strategies, the situation did not change significantly
of the same type strategy and the 'Rush' bots performed better, so the 'Defence' strategies were abandoned.

Then we switched map to 'TwoBasesBarracks16x16' and run the test, the result is shown on the
Table \ref{table:TwoBasesBarracks16x16}.

\input{tables/chap06_TwoBasesBarracks16x16.tex}

From the result we noticed as prediction, the 'Worker' strategies were utterly routed. The reason is
apparently, there are two initial barracks of each player on the map, only training worker is not enough
to beat enemy. On this map, we noticed that 'HeavyRush' is the strongest bot, which means heavy unit is
stronger than other two types attack units. But there is a strange phenomenon that the strategy
'SimpleEconomicRush' failed to beat any bot include 'Worker' bot, which is unexpected. Though analysing
the code structure and battle procedure, we discovered that one rule of 'SimpleEconomicRush' is that the
worker amount depends on the base amount, which is 3 times of base amount. On the map 'TwoBasesBarracks16x16',
there exist two bases of each player, leads to the bot of 'SimpleEconomicRush' would create 6 workers,
finally such amount of workers have possibilities to block the road between base and resource, then the
whole action gets stuck and bot crashed. In order to solve this problem and test the real strength of
'SimpleEconomicRush', we run the test on previous map which only have one base and no barracks for each
player and get rid of 'Worker' strategies(The reason why eliminating 'Worker' is that create a condition
that each player has barracks, but 'Worker' strategies are incapable to build barracks), the situation is
changed, 'SimpleEconomicRush' become the best bot for beating any other 'Rush' bot. Through analysing, the
strength of 'SimpleEconomicRush' including the higher harvesting efficient and variant attack units portfolio.
So when building our tactical bot, under the condition of existing barracks on map, we simulated the
behaviour of 'SimpleEconomicRush' and fixed the relation between worker amount and base amount to avoid
stuck and crash problems.

The final map we tested is 'NoWhereToRun9x8'. In this map, the resource split the map into two parts,
each player located in one side, which means the moveable unit is unable to reach opponent's units or
buildings directly. The only way to get through the path is waiting for the resource unit is exhausted.
The testing result is shown at the Table \ref{table:NoWhereToRun9x8}.

\input{tables/chap06_NoWhereToRun9x8.tex}

From the result we noticed that 'SimpleEconomicRush' still perform best. But there was one thing caught
our attention, the ranged units shown unexpected battle effectiveness on this map, ranged units have the
largest attack range, which make them able to ignore the terrain to cause damage. Because the resource
divide the map into two parts, heavy and light units is unable to get close to ranged but ranged could
attack them. So when we design our strategy, we set up a rule that when the path.
